---
output: rmarkdown::github_document
---

# zdnsr

Perform Bulk 'DNS' Queries Using 'zdns'

## Description

Provides wrapper/helper methods for executing 'zdns'  (<https://github.com/zmap/zdns>) bulk queries along with utility methods to retrieve and cache 'Public DNS' (<http://public-dns.info/>) nameserver lists.

- `zdns`: <https://github.com/zmap/zdns>
- `Public DNS Lists`: <http://public-dns.info/>

## What's Inside The Tin

The following functions are implemented:

- `install_zdns`:	Helper to try to get `zdns` installed
- `refresh_publc_nameservers_list`:	Refresh the list of valid public nameservers
- `zdns_exec`:	Raw interface to `zdns`
- `zdns_help`:	Raw interface to `zdns`
- `zdns_query`:	Bulk query using `zdns`

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/zdnsr")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(zdnsr)

# current verison
packageVersion("zdnsr")

```

